\textsf{Cyp2SQL -- Documentation}

### 2017-08-22 docs/latex/draftB.tex
Bug fixes and more testing and improved documentation.

\subsection{Graph to relational: theory}
\label{ssec:grreltheory}
All the nodes from the graph are stored in one relation (nodes), and all the relationships are stored in a separate relation (edges).

@@

For graph functions to be computable on the relational side, the schema converter also builds two materialised views –- \texttt{adjlist\_from} \& \texttt{adjlist\_to}.

>>>>

\subsection{Graph to relational: theory}
\label{ssec:grreltheory}
All the nodes from the graph are stored in one relation (\emph{Nodes}), and all the relationships are stored in a separate relation (\emph{Edges}).

@@

For graph functions to be computable on the relational side, the schema converter also builds two materialised views –- \texttt{adjlist\_from} \& \texttt{adjlist\_to}. For the performance of the queries to be better when relationships are used, a unique index constraint is added to the \emph{Edges} relation as well. It is recommended to add even further indices where applicable for larger boosts in speed.
